---
title: "Bd_vaccine_ABM"
author: "KM Barnett"
date: "2/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#Current Functionality of Model
-simple pond - leave in as a baseline for a "well-mixed population"
-single pond
-single species
-within season
-daily time step (tick = 1 day)
-2 lifestages: tadpoles and metamorphs
-mortality
  -3 types of mortality
    1) tadpole baseline mortality, 2) metamorph baseline mortality,
    3) Bd-infection induced mortality (read Jager 2011 on this)
-bd transmission (though this needs to be updated)
-no immunity
-tadpole movement:
  - how far do tadpoles move? sphere of influence? list function
  -implement it in a way that movement can be increased or decreased
  -in principle, make it so that tadpole can move 1 to 5+ patches a day 
-do we want to initialize with tadpoles on every patch or tadpoles only on a certain number of patches?
    -equal probability for a tadpole to be on any patch but uniform distribution 
    -intialize density rather than number of tadpoles 
    -multinomial distribution
-infections maintained through metamorphosis: spn on metamorphs is now 10% of what it was as tadpole (3/7/22)
-sporangia loads are capped at s_k in tadpoles (sporangia carrying capacity) and smax in metamorphs (mortality threshold)
      -undecided if smax should be proportional to s_k
   
#investigate   
    -tadpole zoospore shedding submodel
    -metamorph movement - within a timescale step, how far do metamorphs move? land vs. pond

#Minor To Dos:

prioritization of what to implement
1) frog ecology first
2) bd dynamics
3) bd dynamics and baseline/natural immunity
4) vaccination

-tadpole zoospore shedding submodel
-conversion factor from taegan's paper on bd transition through metamorphosis, proportionality or just start with 10%
-update Bd transmission submodel
-Movement: how do we want to represent metamorph movement?
  -run model with extremes of movement
-negative tadpole age to simulate variation in hatching (multiple birth pulses, etc.)
  -tadpoles with age less than zero do not do anything in submodel 

#Major To dos:
-Observation: decide major outputs of interest
    -emerging metmorph population size
    -Bd infection intensity of emerging metamorphs
        -at what time post-emergence? two weeks post-emergence or directly upon emergence?
    -hidden toll - histogram of bd loads for dead frogs
-Observation cont..: other outputs to keep track of:
    -density of zoospores in the pool
    -metamorph infection intensity upon metamorphosis, regardless of survival
    -proportion of all mortality (in both tadpoles and metamorphs or just metamorphs?) attributable to bd
        -not really though because no way to separate - becomes more population regulation by Bd
        -just compare scenarios with and without bd
    -focus observational outputs to ecologically relevant phenomenon
-pattern matching outcomes:
    -life stage distribution over time
    -do the infection intensities follow a negative binomial distribution (with high degree of aggregation, especially in           tadpoles?
    -does prevalence look realistic?
    -does population size seem realistic? (i.e., not a tiny metamorph population size)
-sensitivity analysis based on baseline model?
  -relatively straightforward
-how to represent immunity in the model?
    -3 types of immunity:
      1) baseline immunity, 2) immunity derived from infection clearance, and 3) vaccination immunity
    -waning?
-decide on scenarios to run
-run simulations
-analyze scenario outputs

#Re-add to model:
-tadpole movement
-zoospore + zoosporangium decay


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
