---
title: "Bd_vaccine_ABM"
author: "KM Barnett"
date: "2/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Current Functionality of Model
-simple pond (not needed)
-single pond & multipond landscape
-2 species
-do we want to initialize with tadpoles on every patch or tadpoles only on a certain number of patches?

Minor To Dos:
-add back the things I removed from the model
-update Bd transmission submodel
-zoospore shedding submodel

Major To dos:
-decide major outputs of interest
    -emerging metmorph population size
    -Bd infection intensity of emerging metamorphs

Re-add to model:
-tadpole movement
-zoospore + zoosporangium decay
-baseline tadpole mortality
-metamorphs

Should we remove?
-Simple pond feature
-Multi pond capabilities
-eggs?

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
